```{r}
library("ggplot2")
library("plyr")
library("magrittr")
library("stringr")
library("patchwork")
library("animation")
```



```{r}
transmission_pairs_china = read.csv("C:\\Users\\sedar\\Documents\\Seda_Radoykova\\OneDrive - University College London\\Work\\Oxford_BDI_summer_2021\\Secondary distribution\\Data Catalogue\\seda\\freq_distr\\transmission_pairs_china.csv")
```

```{r}
colnames(transmission_pairs_china)

# sources of data cited
# lots of municipalities, health commissions, etc
transmission_pairs_china$data_source %>% unique #%>% 
#    stringr::str_split(., " ") %>% unlist %>% unique 
```

```{r}
# time frame covered
# contains all dates for infector and infectee symptom onset reports 
c(transmission_pairs_china$infector_onset_date,
         transmission_pairs_china$infectee_onset_date) %>% unique %>% 
    as.Date(., format = "%m/%d/%y") %>% sort %>% range 
# fron "2020-01-07" to "2020-02-28"
```

```{r}
# cities 
c(transmission_pairs_china$infector_reported_city,
  transmission_pairs_china$infector_infected_city, 
  transmission_pairs_china$infectee_reported_city, 
  transmission_pairs_china$infectee_infected_city) %>% unique %>% sort 
```

### Data overview 

- Original data set: 1407 observations. 
- 581 + 698 = 1279 for household/non-household with known infector and infectee age, household info 
- drop further to 332 + 328 = 660 for household/non-household, age and with known infection onset dates


## Household/non-household pre/post lockdown 

```{r}
transmission_pairs = dplyr::select(transmission_pairs_china, pair_id, infector_id, infector_age, infectee_id, infectee_age, is_household, infector_onset_date, infectee_onset_date)
head(transmission_pairs)


transmission_pairs$infector_age = as.integer(transmission_pairs$infector_age)
transmission_pairs$infectee_age = as.integer(transmission_pairs$infectee_age)
transmission_pairs$is_household = as.factor(transmission_pairs$is_household)
transmission_pairs$infector_onset_date = as.Date(transmission_pairs$infector_onset_date, 
                                                 format = "%m/%d/%y")
transmission_pairs$infectee_onset_date =  as.Date(transmission_pairs$infectee_onset_date, 
                                                 format = "%m/%d/%y")
```

```{r}
transmission_pairs$infector_age_bins5 <-
    cut(
        transmission_pairs$infector_age,
        breaks = seq(0, 95, 5),
        include.lowest = TRUE,
        right = FALSE
    )
transmission_pairs$infectee_age_bins5 <-
    cut(
        transmission_pairs$infectee_age,
        breaks = seq(0, 95, 5),
        include.lowest = TRUE,
        right = FALSE
    )

# table(transmission_pairs$infector_age_bins5)
# table(transmission_pairs$infectee_age_bins5)
```


```{r}
transpairs = transmission_pairs[complete.cases(transmission_pairs),]
cust_lab_names = levels(transpairs$infector_age_bins5)
cust_lab_names[seq(2,19,2)] = ""
```

- do we do infector onset < 23 jan OR infector/infectee onset < 23 jan
    - numbers only change after calling complete cases in transpairs above
    - 
    
```{r}
transpairs$lockdown = rep(NA, nrow(transpairs))
transpairs$lockdown = ifelse((transpairs$infector_onset_date <= "2020-01-23" | transpairs$infectee_onset_date <= "2020-01-23"), "pre", "post")
table(transpairs$is_household, transpairs$lockdown, useNA = "always")
```


```{r}
household = transpairs[which(transpairs$is_household == "yes"),]
non_household = transpairs[which(transpairs$is_household != "yes"),]
table(transpairs$is_household)
table(transpairs$lockdown)
```




```{r}
household_pre = household[which(household$infector_onset_date <= "2020-01-23"),]
household_post = household[which(household$infector_onset_date > "2020-01-23"),]
non_household_pre = non_household[which(non_household$infector_onset_date <= "2020-01-23"),]
non_household_post = non_household[which(non_household$infector_onset_date > "2020-01-23"),]

list(household_pre, household_post, non_household_pre, non_household_post) %>% purrr::map(., nrow) #%>% unlist %>% sum
# add to 660 
```


```{r}
plt_fnc = function(.x = household, .title = "Household age/infection matrix")
    ggplot(data = .x, aes(x = infector_age_bins5, y = infectee_age_bins5)) +
    geom_bin2d() +
    labs(x = "Infector age", y = "Infectee age", title = .title) +
    theme_minimal() +
    scale_fill_gradient2(
        low = "gray95",
        mid = "steelblue",
        midpoint = 10,
        limit = c(0, 15),
        space = "Lab"
    ) +
    scale_x_discrete(breaks = levels(household$infector_age_bins5),
                     labels = cust_lab_names) +
    theme(legend.title = element_blank(), legend.position = "none")
```

```{r}
all_data = list(household_pre, non_household_pre, household_post, non_household_post)
all_names = c("Household, pre-lockdown", "Non-household, pre-lockdown", 
              "Household, post-lockdown", "Non-household, post-lockdown")

all_plts = purrr::map2(all_data, all_names, plt_fnc)

all_plts[[1]] + all_plts[[2]] + all_plts[[3]] + all_plts[[4]]
```


```{r}
transpairs$lockdown = factor(transpairs$lockdown, 
                             levels = c("pre", "post"))
transpairs$is_household = factor(transpairs$is_household, 
                                 levels = c("yes", "no"))
```


```{r}
######### LABELS 
house_labs = c(yes = "Household transmission", 
               no = "Non-household transmission")
lock_labs = c(pre = "Pre-lockdown", post = "Post-lockdown")

# facet grid
plt = ggplot(data = transpairs, aes(x = infector_age_bins5, 
                              y = infectee_age_bins5)) +
    geom_bin2d() +
    labs(x = "Infector age", y = "Infectee age") +#, title = .title) +
#    theme_minimal() +
    scale_fill_gradient2(
        low = "gray95",
        mid = "steelblue",
        midpoint = 5,
        limit = c(0, 10),
        breaks = c(0,2,4,6,8,10),
        space = "Lab", name = "Count") +
    scale_x_discrete(breaks = levels(household$infector_age_bins5),
                     labels = cust_lab_names) +
    theme(legend.title = element_blank(), legend.position = "right", 
          axis.text.x = element_text(angle = 15)) + 
    facet_grid(lockdown~is_household, 
               labeller = labeller(is_household = house_labs, 
                                   lockdown = lock_labs))
plt

# ggsave(
#     plt,
#     file = paste0("household_lockdown.png"),
#     width = 20,
#     height = 15,
#     units = "cm"
# )
```

```{r}
table(transpairs$is_household, transpairs$lockdown, useNA = "always")
```


```{r}
### check max coutns in every group to adjust scale colors 
# table( 
#       household$infector_age_bins5,
#       household$infectee_age_bins5,
#       household$lockdown, 
#       useNA = "always")
# table( 
#       non_household$infector_age_bins5,
#       non_household$infectee_age_bins5,
#       non_household$lockdown, 
#       useNA = "no")
```

### Try bootstrapping 

```{r}
plt_single = function(.data, .scale_range = c(0,10)){
    ggplot(data = .data, aes(x = infector_age_bins5, 
                              y = infectee_age_bins5)) +
    geom_bin2d() +
    labs(x = "Infector age", y = "Infectee age") +#, title = .title) +
#    theme_minimal() +
    scale_fill_gradient2(
        low = "gray95",
        mid = "steelblue",
        midpoint = .scale_range[2]/2,
        limit = .scale_range,
        breaks = seq(from = .scale_range[1], 
                     to = .scale_range[2], 
                     length.out = 6),
        space = "Lab", name = "Count") +
    scale_x_discrete(breaks = levels(household$infector_age_bins5),
                     labels = cust_lab_names) +
    theme(legend.title = element_blank(), legend.position = "right", 
          axis.text.x = element_text(angle = 15)) + 
    facet_grid(lockdown~is_household, 
               labeller = labeller(is_household = house_labs, 
                                   lockdown = lock_labs))
}
```


```{r}
## this sample seems to randomise all the data 
### add comma data[,c(cols)] OR data[c(cols)]??????
### this essentially samples from lockdown/no lockdown... 
## should we sample a date and then calculate lockdown/not?? 
        ## i.e. should we simulate some data or just draw samples? 
purrr::map(transpairs[,c("infector_onset_date", 
                              "infectee_onset_date", 
                              "infector_age_bins5", 
                              "infectee_age_bins5",
                              "is_household",
                              "lockdown")], 
       function(x) sample(x, 700, TRUE)) %>% as.data.frame %>% 
    plt_single(., c(0,13))
## lol sometimes it doesn't sample all the labels hahaha
```
```{r}
## this samples from the original groups
transpairs[sample(1:nrow(transpairs), 1000, T), ] %>% 
    plt_single(., c(0,19))
```

### Make gifs 

```{r}
# make plots and save in ggplot objects 

plts = list()
for (i in 1:50) {
    plts[[i]] = transpairs[sample(1:nrow(transpairs), 1000, T), ] %>% 
    plt_single(., c(0,22))
}

#plts

# saveGIF({
#     print(plts)
# }, ani.width = 2362*0.5, ani.height = 1771*0.5, interval = 1/2)
```

```{r}
## use this one for factors!!! 
plt_single = function(.data, .scale_range = c(0,10)){
  .data$lockdown = factor(.data$lockdown, 
                             levels = c("pre", "post"))
  .data$is_household = factor(.data$is_household, 
                                 levels = c("yes", "no"))
  house_labs = c(yes = "Household transmission", 
               no = "Non-household transmission")
  lock_labs = c(pre = "Pre-lockdown", post = "Post-lockdown")
  ggplot(data = .data, aes(x = infector_age_bins5, 
                              y = infectee_age_bins5)) +
    geom_bin2d() +
    labs(x = "Infector age", y = "Infectee age") +#, title = .title) +
#    theme_minimal() +
    scale_fill_gradient2(
        low = "gray95",
        mid = "steelblue",
        midpoint = .scale_range[2]/2,
        limit = .scale_range,
        breaks = seq(from = .scale_range[1], 
                     to = .scale_range[2], 
                     length.out = 6),
        space = "Lab", name = "Count") +
    scale_x_discrete(breaks = levels(household$infector_age_bins5),
                     labels = cust_lab_names) +
    theme(legend.title = element_blank(), legend.position = "right", 
          axis.text.x = element_text(angle = 15)) + 
    facet_grid(lockdown~is_household, 
               labeller = labeller(is_household = house_labs, 
                                   lockdown = lock_labs))
}
```


```{r}
## more randomised data 
plts_bs = list()
for (i in 1:50) {
plts_bs[[i]] = purrr::map(transpairs[,c("infector_onset_date", 
                              "infectee_onset_date", 
                              "infector_age_bins5", 
                              "infectee_age_bins5",
                              "is_household",
                              "lockdown")], 
       function(x) sample(x, 700, TRUE)) %>% as.data.frame %>% 
    plt_single(., c(0,13))
}

# saveGIF({
#     print(plts_bs)
# }, ani.width = 2362*0.5, ani.height = 1771*0.5, interval = 1/2)
```


```{r}
# save gifs
# save(plts, plts_bs, file = "data/boostratp_data.RData")
load("data/boostratp_data.RData")
```



